%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1.1cm,right=1.1cm,top=0.8cm,bottom=1.2cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Mulberry}{HTML}{72243D}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[hidelinks]{hyperref}

\linespread{1}

\begin{document}

\name{Minjie Mao}
\tagline{Student Pursuing Master's Degree}
%\photo{2.8cm}{Globe_High}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:minjiema@usc.edu}{minjiema@usc.edu}}
  \phone{+1 (734) 604-5631}
  \mailaddress{1420 W 22ND ST, Los Angeles, CA 90007}
%  \location{Los Angeles, CA 90007}
	\github{\href{https://github.com/defthobo}{defthobo}}
  \linkedin{\href{https://www.linkedin.com/in/minjie-mao-5b126123a} {LinkedIn}}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection{Education}
\cveducation{University of Southern California}{Los Angeles, USA}{Master of Science in Computer Science | GPA - 3.67/4.00}{Sep 2023 -- May 2025 (Expected)}

\cveducation{University of Michigan - Ann Arbor}{Ann Arbor, USA}{Bachelor of Science in Computer Science (Dual Degree) | GPA - 3.78/4.00}{Sep 2021 -- Apr 2023}


\cveducation{Shanghai Jiao Tong University}{Shanghai, China}{Bachelor of Science in Electrical and Computer Engineering (Dual Degree) | GPA - 3.62/4.00}{Sep 2019 -- Aug 2023}


\cvsection{Technical Skills}
\textbf{Languages:} Python, C/C++, SystemVerilog, JavaScript, TypeScript, Java, Kotlin, Bash Scripting, HTML, CSS\\
\textbf{Frameworks \& Development Tools:} Linux, CUDA, NeuronxDistributed, NodeJS, React, Angular, Bootstrap,Pytorch\\
\textbf{Databases:} SQLite, Oracle, MongoDB 

\vspace{1pt}
\cvsection{Work Experience}

\cvevent{Amazon Web Services}{San Jose, USA}{Software Dev Engineer Intern - Machine Learning Chip Accelerator}{LLM, torchXLA}{May 2024 -- Aug 2024}
\begin{itemize}
	\item Implemented multi-modal model inference on AWS  ML chips (Trn1/Inf2) under NeuronxDistributed framework.
	\item Enabled input and output channel level tensor parallel convolutional layer on neuron device.
	\item Designed preprocessing of the embedding mask on CPU\ to avoid tensor materialization and IR graph truncation.
%	\item Optimized Llava inference throughput by integrating paged KV cache technique for efficient memory management.
\end{itemize}

\cvevent{Shanghai Jiao Tong University}{Shanghai, China}{Engineering Drawing OCR Systems Research Assistant} {Python, PaddleOCR, PyTorch}{Dec 2022 -- Nov 2023}
\begin{itemize}
	\item Augmented data according to test results, including the generation of annotations with complex background.
	\item Added triplet vector embedding techniques to PaddleOCR workflow, improving recognition accuracy to over 80\%.
\end{itemize}


\cvsection{Projects}

\cvevent{}{}{Responsive Web \& Android App Dev}{Typescript, NodeJS, Angular, MongoDB, Kotlin, REST API}{Jan 2024 -- May 2024}
\begin{itemize}
	\item Developed a real-time stock search website with responsive design using Bootstrap and Angular framework. \href{http://stock-env.eba-etbgm9hj.us-west-1.elasticbeanstalk.com/search/home}{\faExternalLink}
	\item Deployed NodeJS backend server and MongoDB Atlas to persistently store user information.
	\item Enabled gesture control features on migrated android stock search application.
\end{itemize}

\cvevent{}{}{Reliable Transport Protocol \& BBR Congestion Control}{C/C++, Socket Programming, Quagga, BBR}{Sep 2023 -- Dec 2023} 
\begin{itemize}
	\item Built a reliable transport protocol on top of UDP with cumulative acknowledgment and sliding window to resolve issues of packet loss, delay, corruption, duplication, and reordering.
	\item Configured OSPF, iBGP and eBGP within an Autonomous System using Quagga routing suite.
	\item Added Bottleneck Bandwidth and Round-trip propagation time(BBR) congestion control protocol to simplified TCP.
\end{itemize}

\cvevent{}{}{R10K-style Out-of-Order Superscalar Processor}{SystemVerilog}{Jan 2023 - Apr 2023}
\begin{itemize}
	\item Oversaw the intricate design of critical components of an R10k-style out-of-order superscalar processor, including the Reorder Buffer (ROB), Reservation Stations (RS), and Physical Register File (PRF) to increase instruction level parallelism.
	\item Implemented a multiport non-blocking instruction cache and an instruction fetcher coordinating with branch predictor.
	\item Engineered a 2-way set-associative data cache featuring a victim cache under LRU policy, to minimize cache misses.
\end{itemize}

\cvevent{}{}{Fakebook Database} {Oracle SQL, MongoDB, Java, JavaScript}{Jan 2023 -- Apr 2023}
\begin{itemize}
	\item Designed an ER Diagram and built a schema of tables from a Facebook-like application database.
	\item Constructed SQL queries using Java and JDBC to extract useful information from fakebook database.
	\item Migrated tables in fakebook database to a MongoDB collection of users and finished queries on the collection.
\end{itemize}

\cvevent{}{}{Optimization of the Neural Network Convolutional Forward Pass}{CUDA C/C++}{Sep 2022 -- Dec 2022}
\begin{itemize}
	\item Adopted shared memory tiling technique to reduce global memory traffic of the forward path of convolutional layers.
	\item Reduced convolution kernel to a highly efficient matrix multiplication kernel with input unfolding and replicating.
	\item Exploited multiple fine-tuned kernels tailored for various convolutional layers within deep learning models.
\end{itemize}

%\cvevent{}{}{Parallel Web Search Engine using MapReduce Framework}{Python, JavaScript, SQLite, Flask, ReactJS}{Jan 2022 -- Apr 2022}
%\begin{itemize}
%	\item Developed a client-side dynamic website with a SQL backend server, employing ReactJS for responsive user interfaces.
%	\item Implemented a pipeline of MapReduce programs to run TF-IDF algorithms for precise search results.
%	\item Engineered UDP-based heartbeat mechanism to swiftly detect system failures and reassign tasks to live servers.
%\end{itemize}

\cvevent{}{}{Operating System Emulation}{C/C++, Multithreading, Network File System}{Sep 2022 -- Dec 2022}
\begin{itemize}
	\item Customized a thread library with mutex support to manage uniprocessor scheduling.
	\item Implemented virtual memory management pager, optimizing memory allocation and resource utilization.
	\item Orchestrated emulation of a multi-threaded, multi-client, and secure network file system server, minimizing disk I/Os.
\end{itemize}










\clearpage
%\cvsection[page2sidebar]{Projects}
%
%
%\begin{itemize}
%\item Film Studies
%
%Analysis of 5 Foreign Language Films, which included, The Lives of Others, The Song of Sparrows, Rashomon, City of God, The Motorcycle Diaries
%
%
%
%\item Documentary
%
%Soul Exchange, Based on Mother's Day - by J.B. Priestely, Worked as an Assistant Director and Camera Person
%
%
%
%\item Video Production
%
%A short short film on 'Growing-up'
%\end{itemize}
%
%
%
%\cvsection{DECLARATION}
%I hereby declare that the above mentioned information is correct up to my
%knowledge and I bear the responsibility for the correctness of the above mentioned.
%
%\medskip
%
%
%\cvevent{}{}{Date - 23.02.19}{Place - New Delhi}
%
%
%
%%% If the NEXT page doesn't start with a \cvsection but you'd
%%% still like to add a sidebar, then use this command on THIS
%%% page to add it. The optional argument lets you pull up the 
%%% sidebar a bit so that it looks aligned with the top of the
%%% main column.
%% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}
